Comparaciones Teórico-Experimental

### 2015-11-19 ComparisonsMain.Rmd
cambie ComparisonsMain.Rmd y comp_input.csv

# Read Input.
input <- read.csv("DATA/comp_input.csv")
family <- input$family[1]
p.ref <- input$p.ref[1]
heme <- input$heme[1]
core <- input$core[1]
index = as.vector(input$index)

@@

# Read experimental output.
dir.e <- "OUT/Experimental"
if (as.character(family) == "globins") {
  family <- paste(family, "_heme_", heme, sep = "")
}
m.Pne = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
Pne.mean = colMeans(m.Pne)
m.Qne = t(apply(m.Pne, 1, cumsum))
Qne.mean = colMeans(m.Qne)
m.evaluese = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
evaluese.mean = colMeans(m.evaluese)
ievaluese.mean = 1/evaluese.mean
laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
MSD = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_MSD.csv", sep = "")))$x
id = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.ID.csv", sep = "")))$x
id.index = id[index]

>>>>

# Read Input.
input <- read.csv("DATA/comp_input.csv")
family <- input$family[1]
p.ref <- input$p.ref[1]
heme <- input$heme[1]
core <- input$core[1]

@@

# Read experimental output.
dir.e <- "OUT/Experimental"
if (as.character(family) == "globins") {
  family <- paste(family, "_heme_", heme, sep = "")
}
laligned = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.laligned.csv", sep = "")))$x
  index <- c()
  for (i in (1:length(laligned))) {
    if (laligned[i] == max(laligned)) {
      index[i] <- i
    }
  }
index <- index[!is.na(index)]
m.Pne = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.Pn.csv", sep = "")))[index, 1:nmodes4]
Pne.mean = colMeans(m.Pne)
m.Qne = t(apply(m.Pne, 1, cumsum))
Qne.mean = colMeans(m.Qne)
m.evaluese = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.evalues.csv", sep = "")))[index, 1:nmodes4]
evaluese.mean = colMeans(m.evaluese)
ievaluese.mean = 1/evaluese.mean

MSD = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_MSD.csv", sep = "")))$x
id = read.csv(file.path(dir.e, paste(family, "_core_", core, "_out_m.ID.csv", sep = "")))$x
id.index = id[index]
